### 2012-05-17 GUIErrorDetector/paper/evaluation.tex
improve sentences
small wording tweak

We submitted all \newbugs new errors to the respective developers. As of May 2012, 
1 error S3dropbox has been confirmed, and we have reproduced other errors,
in which 2 errors in FileBunker and ArecaBackup
have not yet been verified by the developers. 
%2 errors in SudokuSolver can be reproduced by simply
%clicking its UIs, and the rest 4 errors can be reproduced
%by writing a test driver have not yet been verified
%by the developers.
All found bugs and our experimental results are
publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
We ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths
on average, but did not output any real errors before it terminated.
The number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible to enumerate all paths for a realistic call graph.
In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
of each node is 2.15. Thus, a rough estimation for the number of distinct
non-cyclic paths leads to an astronomically large number: 
$2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.

>>>>

We submitted all \newbugs new errors to the respective developers. As of May 2012, 
1 error S3dropbox has been confirmed, and we have reproduced other errors.
All found bugs and our experimental results are
publicly available at: \url{http://www.cs.washington.edu/homes/szhang/guierror/}.
%in which 2 errors in FileBunker and ArecaBackup
%have not yet been verified by the developers. 
%2 errors in SudokuSolver can be reproduced by simply
%clicking its UIs, and the rest 4 errors can be reproduced
%by writing a test driver have not yet been verified
%by the developers.

@@

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
We ran this variant on each subject for 1 hour, it explored 5.1$\times$$10^9$ paths
on average, but did not output any real errors before it terminated.
The number of non-cyclic paths in a graph is exponential in the graph size,
and it is infeasible to enumerate all paths for a realistic call graph.
In our experiments, the smallest call graph contains 7201 nodes and the average out-degree
of each node is 2.15. Thus, a rough estimation for the number of distinct
non-cyclic paths gives an astronomically large number: 
$2.15^{7201}$ $\approx$ 1.07$\times$$10^{2107}$.
